---
title: "p8105_homework1_yx2858"
author: "Yueyi Xu"
date: "2023-09-22"
output: html_document
---

```{r setup, include = FALSE}
library(tidyverse)
```

#Problem 1

```{r}
library(moderndive) #load library moderndive
data("early_january_weather") #load data "early_january_weather"
mean(early_january_weather$temp) #calculate the mean for temperature
ggplot(early_january_weather, aes(x = time_hour, y = temp, color = humid)) + geom_point() #graph the scatterplot
ggsave("early_january_weather.pdf") #save the scatterplot in pdf format
```

Description of the dataset:
The dataset contains several variables including year, month, day, hour, temperature, humid, wind direction, wind speed, wind gust, and etc. The size of the dataset can be found using nrow and ncol in r code. In this dataset, the number of rows is 348, and the number of columns (variables) is 15. The mean temperature in the dataset is calculated using the above code mean(early_january_weather$temp) which is 39.58212 in degrees Fahrenheit.


#Problem 2
Create a dataframe:
```{r create_df}
df =
  tibble(
    v_sample = rnorm(10), #random sample size of 10
    v_logical = v_sample > 0, #a logical vector indicating whether the elements of the sample are greater than 0
    v_character = c("A", "B", "C", "D", "E", "F", "G", "H", "I", "J"), #a character vector of length 10
    v_factor = factor(c("low", "low", "low", "medium", "medium", "medium", "medium", "high", "high", "high")) #a factor vector of length 10 with 3 different "levels"
  )
```

Take the mean of each variables in dataframe:
```{r}
mean(pull(df, v_sample)) #calculate the mean of sample size
mean(pull(df, v_logical)) #calculate the mean of logical vector
mean(pull(df, v_character)) #calculate the mean of character vector
mean(pull(df, v_factor)) #calculate the mean of factor vector
```
The mean of v_sample and v_logical works, but the mean of v_character and v_factor does not work.

Apply "as.numeric" function to the logical, character, and factor variables:
```{r}
as.numeric(pull(df, v_logical)) #convert logical vector to numeric
as.numeric(pull(df, v_character)) #convert character vector to numeric
as.numeric(pull(df, v_factor)) #convert factor vector to numeric
```
Logical vector and factor vector are successfully converted to numeric; however, character vector cannot be converted to numeric because it is not a numeric variable. This explains why character vector and factor vector did not work when calculating the mean value.

